An equivalence of compositional frameworks

### 2018-09-28 EquivCompFrameworks_20180911kc.tex
initial3
mainly condensing diagrams

@@

In Fong's theory of decorated cospans, given a category $\bold{C}$ with finite colmits, a symmetric lax monoidal functor $F \colon (\bold{C},+,0) \to (\bold{D},\otimes,I)$ is used to `decorate' the apex of a cospan in $\bold{C}$ with an element of the image of its apex under the functor $F$, in the case of the first cospan above, a morphism $d \colon I \to F(c)$. Here $F(c)$ is the collection of all $F$-decorations on the object $c$ and the morphism $d$ is selecting a particular one. Thus a decorated cospan is then a pair:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,1) {$c$};
\node (C) at (2,0) {$b$};
\node (D) at (3,0.5) {$I$};
\node (E) at (4,0.5) {$F(c)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B)
(D) edge node [above] {$d$} (E);
\end{tikzpicture}
\]
To obtain a decoration on the composition of two composable $F$-decorated cospans:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,1) {$c$};
\node (C) at (2,0) {$b$};
\node (F) at (3,0) {$b$};
\node (G) at (4,1) {$f$};
\node (H) at (5,0) {$e$};
\node (D) at (0.5,-0.5) {$I$};
\node (E) at (1.5,-0.5) {$F(c)$};
\node (D') at (3.5,-0.5) {$I$};
\node (E') at (4.5,-0.5) {$F(f)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B)
(F) edge node[above]{$i^\prime$} (G)
(H) edge node[above]{$o^\prime$} (G)
(D) edge node [above] {$d_1$} (E)
(D') edge node [above] {$d_2$} (E');
\end{tikzpicture}
\]
we use the natural map from a coproduct to a pushout as well as the natural map that comes as part of the structure of a lax monoidal functor:
 $$1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{d_1 \times d_2} F(c) \times F(f) \xrightarrow{\phi_{c,f}} F(c+ f) \xrightarrow{F(j_{c,f})} F(c+_b f).$$

@@

One approach to remedying this nuisance is to instead view $F$ as a functor $F \colon\bold{C} \to \bold{Cat}$ and then consider $F(c)$ not as a \emph{set} of decorations on the element $c$ but as a \emph{category} of decorations on the element $c$. Then one can construct a similar symmetric monoidal category similar to Fong's, which by similarity and an abuse of notation we also call $F\textnormal{Cospan}(\bold{C})$. This symmetric monoidal category will have:
\begin{enumerate}
\item{objects as those of $\bold{C}$ and}
\item{morphisms as isomorphism classes of cospans of $\bold{C}$ together with an element of image of the apex under the functor $F$.
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,1) {$c$};
\node (C) at (2,0) {$b$};
\node (D) at (3,0.5) {$d \in F(c)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B);
\end{tikzpicture}
\]
Except now, given another morphism:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,-1) {$c^\prime$};
\node (C) at (2,0) {$b$};
\node (D) at (3,-0.5) {$d^\prime \in F(c^\prime)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[below]{$i^\prime$} (B)
(C) edge node[below]{$o^\prime$} (B);
\end{tikzpicture}
\]
these two morphisms are in the same isomorphism class if the following diagrams commute
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,1) {$c$};
\node (B') at (1,-1) {$c^\prime$};
\node (C) at (2,0) {$b$};
\node (D) at (3,0) {$\bold{1}$};
\node (E) at (4,0.5) {$F(c)$};
\node (E') at (4,-0.5) {$F(c^\prime)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B)
(A) edge node[below]{$i^\prime$} (B')
(C) edge node[below]{$o^\prime$} (B')
(B) edge node [left] {$f$} (B')
(D) edge node [above] {$d$} (E)
(D) edge node [below] {$d^\prime$} (E')
(E) edge node [right] {$F(f)$} (E');
\end{tikzpicture}
\]
and there exists an isomorphism $\iota \colon F(f)(d) \to d^\prime$ in the category $F(c^\prime)$.
}
\end{enumerate}
Note that the existence of an isomorphism $\iota \colon F(f)(d) \to d^\prime$ is equivalent to the triangle above on the right commuting up to a 2-isomorphism.
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (4,0) {$\iota \Swarrow$};
\node (D) at (3,0) {$\bold{1}$};
\node (E) at (4.5,1) {$F(c)$};
\node (E') at (4.5,-1) {$F(c^\prime)$};
\path[->,font=\scriptsize,>=angle 90]
(D) edge node [above] {$d$} (E)
(D) edge node [below] {$d^\prime$} (E')
(E) edge node [right] {$F(f)$} (E');
\end{tikzpicture}
\]
In other words, the isomorphism $\iota$ is a \emph{natural} isomorphism. We will typically just write this as $\iota \colon F(f)(d) \to d^\prime$ to conserve space.

@@

\section{A review of double categories and symmetric monoidal double categories}
This section is meant to serve as a review of double categories and to present the definitions of double category, symmetric monoidal double category and a few more ideas that will be used later in the paper. Nothing in this section is new and can be found in the work of Shulman \cite{Shul}.

@@

@@

\node (E) at (-1,0.5) {$c \mapsto$};

@@

\node (D) at (3,0.5) {$I \in F(c)$};

@@

Given two composable horizontal 1-cells:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,1) {$c$};
\node (C) at (2,0) {$b$};
\node (D) at (1,-0.5) {$d \in F(c)$};
\node (E) at (3,0) {$b$};
\node (F) at (4,1) {$c^\prime$};
\node (G) at (5,0) {$e$};
\node (H) at (4,-0.5) {$d^\prime \in F(c^\prime)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B)
(E) edge node[above]{$i^\prime$} (F)
(G) edge node[above]{$o^\prime$} (F);
\end{tikzpicture}
\]
the composite is given by:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,1) {$c$};
\node (C) at (2,0) {$b$};
\node (D) at (3,1) {$c^\prime$};
\node (E) at (4,0) {$e$};
\node (F) at (2,2) {$c+c^\prime$};
\node (G) at (2,3) {$c+_{b} c^\prime$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B)
(C) edge node [above] {$i^\prime$} (D)
(E) edge node [above] {$o^\prime$} (D)
(B) edge node [above] {$j$} (F)
(D) edge node [above] {$j^\prime$} (F)
(F) edge node [left] {$\psi$} (G)
(A) edge node [left] {$\psi j i$} (G)
(E) edge node [right] {$\psi j^\prime o^\prime$} (G);
\end{tikzpicture}
\]
with the corresponding decoration of the apex $\hat{d} \in F(c+_b c^\prime)$ given by:
$$1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{d \times d^\prime} F(c) \times F(c^\prime) \xrightarrow{\phi_{c,c^\prime}} F(c+c^\prime) \xrightarrow{F(\psi)} F(c+_{b}c^\prime)$$
where $\psi \colon c + c^\prime \to c+_b c^\prime$ is the natural map from the coproduct to the pushout and $\phi_{c,c^\prime} \colon F(c) \times F(c^\prime) \to F(c+c^\prime)$ is the natural transformation of the symmetric lax monoidal pseudofunctor $F \colon \bold{C} \to \bold{Cat}$. Denoting the first and second of these horizontal 1-cells as $M$ and $N$, respectively, the source and target structure functors satisfy the equations $S(N \odot M)=S(M)$ and $T(N \odot M)=T(N)$.

@@

\node (F) at (4,1) {$c^\prime$};

@@

\node (J) at (7,1) {$c''$};

@@

(C) edge node[left]{$\id_f$} (C')

@@

@@

where $!_b = F(!)  \phi \colon \bold{1} \to F(b)$ is the trivial decoration on $b$. Composing these then gives:

@@

\node (B) at (1,1) {$c+_b b$};

@@

\node (D) at (3,0.5) {$\hat{d} \in F(c +_b b)$};
(C) edge node[right]{$j \psi_b$} (B);

@@

where the middle square commutes since $F$ is a lax monoidal pseudofunctor and the right square commutes as the underlying diagram commutes. The objects $d_{1,2}$ and $d^\prime_{1,2}$ are given by top and bottom composite of arrows and the morphism of decorations $\iota_{1,2}$ is given by composing $\iota_1 \times \iota_2$ with the two commuting squares. Returning the interchange law, composing the two horizontal compositions above vertically then results in:

@@

@@

@@

\node (D) at (3.5,0.5) {$d_{M_1 \otimes M_2} \in F(c_1+c_2)$};

@@

\node (B) at (1,1) {$0$};

@@

\node (D) at (3,0.5) {$! \in F(0)$};

@@

\node (F) at (4,1) {$c$};

@@

\node (B) at (1,1) {$0+c$};

@@

\node (D) at (3,0.5) {$d^\prime \in F(0+c)$};
(A) edge node[left]{$!+i$} (B)
(C) edge node[right]{$!+o$} (B);

@@

Given a horizontal 1-cell $M$ of $\mathbb{F} \textnormal{Cospan}(\bold{C})$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$c_1$};
\node (B) at (1,1) {$c$};
\node (C) at (2,0) {$c_2$};
\node (D) at (1,-0.5) {$d \in F(c)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$I$} (B)
(C) edge node[above]{$O$} (B);
\end{tikzpicture}
\]
the image $\mathbb{G}(M)$ is the horizontal 1-cell in $_L \mathbb{C}\textnormal{sp}(\bold{D})$ given by:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$L(c_1)$};
\node (B) at (1,1) {$d$};
\node (C) at (2,0) {$L(c_2)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[left]{$L(I)$} (B)
(C) edge node[right]{$L(O)$} (B);
\end{tikzpicture}
\]
and similarly, given a 2-morphism $(f,h,g,\iota) \colon M \to M^\prime$ of $\mathbb{F} \textnormal{Cospan}(\bold{C})$:
\[
\begin{tikzpicture}[scale=1.5]
\node (D) at (1,0.5) {$d \in F(c)$};
\node (D') at (1,-1.5) {$d^\prime \in F(c^\prime)$};
\node (A) at (0,0) {$c_1$};
\node (B) at (1,0) {$c$};
\node (C) at (2,0) {$c_2$};
\node (A') at (0,-1) {$c_1^\prime$};
\node (B') at (1,-1) {$c^\prime$};
\node (C') at (2,-1) {$c_2^\prime$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$I$} (B)
(C) edge node[above]{$O$} (B)
(A') edge node[above]{$I^\prime$} (B')
(C') edge node[above]{$O^\prime$} (B')
(A) edge node [left]{$f$} (A')
(B) edge node [left]{$h$} (B')
(C) edge node [left]{$g$} (C');
\end{tikzpicture}
\]
$$\iota \colon F(h)(d) \to d^\prime$$
the image in $_L \mathbb{C}\textnormal{sp}(\bold{D})$ is given by the 2-morphism:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$L(c_1)$};
\node (B) at (1,0) {$d$};
\node (C) at (2,0) {$L(c_2)$};
\node (A') at (0,-1) {$L(c_1^\prime)$};
\node (B') at (1,-1) {$d^\prime$};
\node (C') at (2,-1) {$L(c_2^\prime)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$L(I)$} (B)
(C) edge node[above]{$L(O)$} (B)
(A') edge node[above]{$L(I^\prime)$} (B')
(C') edge node[above]{$L(O^\prime)$} (B')
(A) edge node [left]{$L(f)$} (A')
(B) edge node [left]{$\alpha$} (B')
(C) edge node [left]{$L(g)$} (C');
\end{tikzpicture}
\]
where $\alpha \colon d \to d^\prime$ is a morphism in the Grothendieck construction of $F$ given by $\alpha = (h \colon c \to c^\prime, \iota \colon F(h)(d) \to d^\prime)$.

Next, we exhibit natural isomorphisms $\eta \colon \id_{ _L \mathbb{C}\textnormal{sp}(\bold{D})} \cong \mathbb{G} \mathbb{E}$ and $\epsilon \colon \mathbb{E} \mathbb{G} \cong \id_{\mathbb{F}\textnormal{Cospan}(\bold{C})}$. First we compute the composites $\mathbb{G} \mathbb{E}$ and $\mathbb{E} \mathbb{G}$. On the object categories, both composites are $\id_\bold{C}$ and we have natural isomorphism $\eta \colon \id_{\bold{C}} \cong \mathbb{G}_0 \mathbb{E}_0$ and $\epsilon \colon \mathbb{E}_0 \mathbb{G}_0 \cong \id_{\bold{C}}$.

Given a horizontal 1-cell $M$ in $_L \mathbb{C} \textnormal{sp}(\bold{D})$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$L(c_1)$};
\node (B) at (1,1) {$d$};
\node (C) at (2,0) {$L(c_2)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B);
\end{tikzpicture}
\]
the horizontal 1-cell $\mathbb{E}(M)$ is given by:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$c_1$};
\node (B) at (1,1) {$R(d)$};
\node (C) at (2,0) {$c_2$};
\node (D) at (1,-0.5) {$d \in F(R(d))$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[left]{$R(i)$} (B)
(C) edge node[right]{$R(o)$} (B);
\end{tikzpicture}
\]
and then the horizontal 1-cell $\mathbb{G} \mathbb{E}(M)$ is given by:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$L(c_1)$};
\node (B) at (1,1) {$d$};
\node (C) at (2,0) {$L(c_2)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[left]{$L(R(i))$} (B)
(C) edge node[right]{$L(R(o))$} (B);
\end{tikzpicture}
\]
\textbf{What can we say about LR? Find a 2-iso between these in $_L Csp(D)$.}
Then we can find a 2-isomorphism $\eta \colon M \xrightarrow{\sim} \mathbb{G}\mathbb{E}(M) $ in $_L \mathbb{C} \textnormal{sp}(\bold{C})$ given by:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$L(c_1)$};
\node (B) at (1,0) {$d$};
\node (C) at (2,0) {$L(c_2)$};
\node (A') at (0,-1) {$L(c_1)$};
\node (B') at (1,-1) {$d$};
\node (C') at (2,-1) {$L(c_2)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B)
(A') edge node[above]{$L(R(i))$} (B')
(C') edge node[above]{$L(R(o))$} (B')
(A) edge node [left]{$1$} (A')
(B) edge node [left]{$1$} (B')
(C) edge node [left]{$1$} (C');
\end{tikzpicture}
\]

>>>>

git pro coming through!

@@

In Fong's theory of decorated cospans, given a category $\bold{C}$ with finite colmits, a symmetric lax monoidal functor $F \colon (\bold{C},+,0) \to (\bold{D},\otimes,I)$ is used to `decorate' the apex of a cospan in $\bold{C}$ with an element of the image of its apex under the functor $F$, in the case of the first cospan above, a morphism $d \colon I \to F(c)$. Here $F(c)$ is the collection of all $F$-decorations on the object $c$ and the morphism $d$ is selecting a particular one. Thus a decorated cospan is given by a pair:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,0) {$c$};
\node (C) at (2,0) {$b$};
\node (D) at (3,0) {$I$};
\node (E) at (4,0) {$F(c)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B)
(D) edge node [above] {$d$} (E);
\end{tikzpicture}
\]
To obtain a decoration on the composition of two composable $F$-decorated cospans:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,0) {$c$};
\node (C) at (2,0) {$b$};
\node (F) at (3,0) {$b$};
\node (G) at (4,0) {$f$};
\node (H) at (5,0) {$e$};
\node (D) at (0.5,-0.5) {$I$};
\node (E) at (1.5,-0.5) {$F(c)$};
\node (D') at (3.5,-0.5) {$I$};
\node (E') at (4.5,-0.5) {$F(f)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B)
(F) edge node[above]{$i^\prime$} (G)
(H) edge node[above]{$o^\prime$} (G)
(D) edge node [above] {$d_1$} (E)
(D') edge node [above] {$d_2$} (E');
\end{tikzpicture}
\]
we use the natural map from a coproduct to a pushout as well as the natural map that comes as part of the structure of a lax monoidal functor:
 $$1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{d_1 \times d_2} F(c) \times F(f) \xrightarrow{\phi_{c,f}} F(c+ f) \xrightarrow{F(j_{c,f})} F(c+_b f).$$

@@

One approach to remedying this nuisance is to instead view $F$ as a functor $F \colon\bold{C} \to \bold{Cat}$ and then consider $F(c)$ not as a \emph{set} of decorations on the element $c$ but as a \emph{category} of decorations on the element $c$. Then one can construct a similar symmetric monoidal category similar to Fong's, which by similarity and an abuse of notation we also call $F\textnormal{Cospan}(\bold{C})$. This symmetric monoidal category will have:
\begin{enumerate}
\item{objects as those of $\bold{C}$ and}
\item{morphisms as isomorphism classes of cospans of $\bold{C}$ together with an element of image of the apex under the functor $F$.
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,0) {$c$};
\node (C) at (2,0) {$b$};
\node (D) at (3,0) {$d \in F(c)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B);
\end{tikzpicture}
\]
Except now, given another morphism:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,0) {$c^\prime$};
\node (C) at (2,0) {$b$};
\node (D) at (3,0) {$d^\prime \in F(c^\prime)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i^\prime$} (B)
(C) edge node[above]{$o^\prime$} (B);
\end{tikzpicture}
\]
these two morphisms are in the same isomorphism class if the following diagrams commute
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,1) {$c$};
\node (B') at (1,-1) {$c^\prime$};
\node (C) at (2,0) {$b$};
\node (D) at (3,0) {$\bold{1}$};
\node (E) at (4,0.5) {$F(c)$};
\node (E') at (4,-0.5) {$F(c^\prime)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B)
(A) edge node[below]{$i^\prime$} (B')
(C) edge node[below]{$o^\prime$} (B')
(B) edge node [left] {$f$} (B')
(D) edge node [above] {$d$} (E)
(D) edge node [below] {$d^\prime$} (E')
(E) edge node [right] {$F(f)$} (E');
\end{tikzpicture}
\]
and there exists an isomorphism $\iota \colon F(f)(d) \to d^\prime$ in the category $F(c^\prime)$.
}
\end{enumerate}
Note that the existence of an isomorphism $\iota \colon F(f)(d) \to d^\prime$ is equivalent to the triangle above on the right commuting up to a 2-isomorphism.
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (4,0) {$\iota \Swarrow$};
\node (D) at (3,0) {$\bold{1}$};
\node (E) at (4.5,1) {$F(c)$};
\node (E') at (4.5,-1) {$F(c^\prime)$};
\path[->,font=\scriptsize,>=angle 90]
(D) edge node [above] {$d$} (E)
(D) edge node [below] {$d^\prime$} (E')
(E) edge node [right] {$F(f)$} (E');
\end{tikzpicture}
\]
In other words, the isomorphism $\iota$ is a \emph{natural} isomorphism. We will typically just write this as $\iota \colon F(f)(d) \to d^\prime$ to conserve space.

@@

\section{A review of double categories and symmetric monoidal double categories}
\textbf{Likely move this to an appendix or remove entirely and just cite another paper.}
This section is meant to serve as a review of double categories and to present the definitions of double category, symmetric monoidal double category and a few more ideas that will be used later in the paper. Nothing in this section is new and can be found in the work of Shulman \cite{Shul}.

@@

\textbf{Likely delete everything in this section before this line.}

@@

\node (E) at (-1,0) {$c \mapsto$};

@@

\node (D) at (3,0) {$I \in F(c)$};
(C) edge node[above]{$1$} (B);

@@

Given two composable horizontal 1-cells:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,0) {$c$};
\node (C) at (2,0) {$b$};
\node (D) at (1,-0.5) {$d \in F(c)$};
\node (E) at (3,0) {$b$};
\node (F) at (4,0) {$c^\prime$};
\node (G) at (5,0) {$e$};
\node (H) at (4,-0.5) {$d^\prime \in F(c^\prime)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B)
(E) edge node[above]{$i^\prime$} (F)
(G) edge node[above]{$o^\prime$} (F);
\end{tikzpicture}
\]
the composite is given by:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,1) {$c$};
\node (C) at (2,0) {$b$};
\node (D) at (3,1) {$c^\prime$};
\node (E) at (4,0) {$e$};
\node (F) at (2,2) {$c+c^\prime$};
\node (G) at (2,3) {$c+_{b} c^\prime$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B)
(C) edge node [above] {$i^\prime$} (D)
(E) edge node [above] {$o^\prime$} (D)
(B) edge node [above] {$j$} (F)
(D) edge node [above] {$j^\prime$} (F)
(F) edge node [left] {$\psi$} (G)
(A) edge node [left] {$\psi j i$} (G)
(E) edge node [right] {$\psi j^\prime o^\prime$} (G);
\end{tikzpicture}
\]
with the corresponding decoration of the apex $\hat{d} \in F(c+_b c^\prime)$ given by:
$$1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{d \times d^\prime} F(c) \times F(c^\prime) \xrightarrow{\phi_{c,c^\prime}} F(c+c^\prime) \xrightarrow{F(\psi)} F(c+_{b}c^\prime)$$
where $\psi \colon c + c^\prime \to c+_b c^\prime$ is the natural map from the coproduct to the pushout and $\phi_{c,c^\prime} \colon F(c) \times F(c^\prime) \to F(c+c^\prime)$ is the natural transformation of the symmetric lax monoidal pseudofunctor $F \colon \bold{C} \to \bold{Cat}$. Denoting the first and second of these horizontal 1-cells as $M$ and $N$, respectively, the source and target structure functors satisfy the equations $S(N \odot M)=S(M)$ and $T(N \odot M)=T(N)$.

@@

\node (F) at (4,0) {$c^\prime$};

@@

\node (J) at (7,0) {$c''$};

@@

@@

\node (F) at (4,0) {$b$};

@@

where $!_b = F(!)  \phi \colon 1 \to F(b)$ is the trivial decoration on $b$. Composing these then gives:

@@

\node (B) at (1,0) {$c+_b b$};

@@

\node (D) at (3,0) {$\hat{d} \in F(c +_b b)$};
(C) edge node[above]{$j \psi_b$} (B);

@@

where the middle square commutes since $F$ is a lax monoidal pseudofunctor and the right square commutes as the underlying diagram commutes. The objects $d_{1,2}$ and $d^\prime_{1,2}$ are given by top and bottom composite of arrows and the morphism of decorations $\iota_{1,2}$ is given by composing $\iota_1 \times \iota_2$ with the two commuting squares. Returning to the interchange law, composing the two horizontal compositions above vertically then results in:

@@

\node (B) at (1,0) {$c_1$};

@@

\node (F) at (4,0) {$c_2$};

@@

\node (B) at (1.25,0) {$c_1+c_2$};
\node (C) at (2.5,0) {$b_1+b_2$};
\node (D) at (4.25,0) {$d_{M_1 \otimes M_2} \in F(c_1+c_2)$};
(A) edge node[above]{$i_1+i_2$} (B)
(C) edge node[above]{$o_1+o_2$} (B);

@@

\node (B) at (1,0) {$0$};

@@

\node (D) at (3,0) {$! \in F(0)$};

@@

\node (F) at (4,0) {$c$};

@@

\node (B) at (1,0) {$0+c$};

@@

\node (D) at (3.5,0) {$d^\prime \in F(0+c)$};
(C) edge node[above]{$!+o$} (B);

@@

Given a horizontal 1-cell $M$ of $\mathbb{F} \textnormal{Cospan}(\bold{C})$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$c_1$};
\node (B) at (1,1) {$c$};
\node (C) at (2,0) {$c_2$};
\node (D) at (1,-0.5) {$d \in F(c)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$I$} (B)
(C) edge node[above]{$O$} (B);
\end{tikzpicture}
\]
the image $\mathbb{G}(M)$ is the horizontal 1-cell in $_L \mathbb{C}\textnormal{sp}(\bold{D})$ given by:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$L(c_1)$};
\node (B) at (1,1) {$d$};
\node (C) at (2,0) {$L(c_2)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[left]{$\tau_c L(I)$} (B)
(C) edge node[right]{$\tau_ c L(O)$} (B);
\end{tikzpicture}
\]
where $\tau_c \colon L(c) \to d$ is the unique morphism from the trival decoration on $c$ given by $$!_c \coloneqq 1 \xrightarrow{\phi} F(0) \xrightarrow{F(!)} F(c)$$ to $d \in F(c)$. In other words, the trivial decoraction $!_c$ is initial in $F(c)$ and $\tau_c \colon !_c \to d$ is the unique morphism to $d$. Similarly, given a 2-morphism $(f,h,g,\iota) \colon M \to M^\prime$ of $\mathbb{F} \textnormal{Cospan}(\bold{C})$:
\[
\begin{tikzpicture}[scale=1.5]
\node (D) at (1,0.5) {$d \in F(c)$};
\node (D') at (1,-1.5) {$d^\prime \in F(c^\prime)$};
\node (A) at (0,0) {$c_1$};
\node (B) at (1,0) {$c$};
\node (C) at (2,0) {$c_2$};
\node (A') at (0,-1) {$c_1^\prime$};
\node (B') at (1,-1) {$c^\prime$};
\node (C') at (2,-1) {$c_2^\prime$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$I$} (B)
(C) edge node[above]{$O$} (B)
(A') edge node[above]{$I^\prime$} (B')
(C') edge node[above]{$O^\prime$} (B')
(A) edge node [left]{$f$} (A')
(B) edge node [left]{$h$} (B')
(C) edge node [left]{$g$} (C');
\end{tikzpicture}
\]
$$\iota \colon F(h)(d) \to d^\prime$$
the image in $_L \mathbb{C}\textnormal{sp}(\bold{D})$ is given by the 2-morphism:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$L(c_1)$};
\node (B) at (1,0) {$d$};
\node (C) at (2,0) {$L(c_2)$};
\node (A') at (0,-1) {$L(c_1^\prime)$};
\node (B') at (1,-1) {$d^\prime$};
\node (C') at (2,-1) {$L(c_2^\prime)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$\tau_c L(I)$} (B)
(C) edge node[above]{$\tau_c L(O)$} (B)
(A') edge node[above]{$\tau_{c^\prime} L(I^\prime)$} (B')
(C') edge node[above]{$\tau_{c^\prime} L(O^\prime)$} (B')
(A) edge node [left]{$L(f)$} (A')
(B) edge node [left]{$\alpha$} (B')
(C) edge node [left]{$L(g)$} (C');
\end{tikzpicture}
\]
where $\alpha \colon d \to d^\prime$ is a morphism in the Grothendieck construction of $F$ given by $\alpha = (h \colon c \to c^\prime, \iota \colon F(h)(d) \to d^\prime)$.

Next, we exhibit natural isomorphisms $\eta \colon \id_{ _L \mathbb{C}\textnormal{sp}(\bold{D})} \cong \mathbb{G} \mathbb{E}$ and $\epsilon \colon \mathbb{E} \mathbb{G} \cong \id_{\mathbb{F}\textnormal{Cospan}(\bold{C})}$. Specifically, these are double natural isomorphisms given by double transformations $\eta$ and $\epsilon$ whose components are isomorphisms.

First we compute the composites $\mathbb{G} \mathbb{E}$ and $\mathbb{E} \mathbb{G}$. On the object categories, both composites are $\id_\bold{C}$ and we have natural isomorphisms $\eta \colon \id_{\bold{C}} \cong \mathbb{G}_0 \mathbb{E}_0$ and $\epsilon \colon \mathbb{E}_0 \mathbb{G}_0 \cong \id_{\bold{C}}$.

Given a horizontal 1-cell $M$ in $_L \mathbb{C} \textnormal{sp}(\bold{D})$:
the horizontal 1-cell $\mathbb{E}(M)$ is given by:
\node (D) at (1,-0.5) {$d \in F(R(d))$};
and then the horizontal 1-cell $\mathbb{G} \mathbb{E}(M)$ is given by:
(A) edge node[left]{$\tau_{R(d)}L(R(i))$} (B)
(C) edge node[right]{$\tau_{R(d)}L(R(o))$} (B);
\textbf{What can we say about LR? Find a 2-iso between these in $_L Csp(D)$.}
Then we can find a 2-isomorphism $\eta_M \colon M \xrightarrow{\sim} \mathbb{G}\mathbb{E}(M) $ in $_L \mathbb{C} \textnormal{sp}(\bold{C})$ given by:
\node (B) at (1.25,0) {$d$};
\node (C) at (2.5,0) {$L(c_2)$};
\node (A') at (0,-1) {$L(c_1)$};
\node (B') at (1.25,-1) {$d$};
\node (C') at (2.5,-1) {$L(c_2)$};
(A') edge node[above]{$\tau_{R(d)}L(R(i))$} (B')
(C') edge node[above]{$\tau_{R(d)}L(R(o))$} (B')
On the other hand, given a horizontal 1-cell $N$ in $\mathbb{F}\textnormal{Cospan}(\bold{C})$:
(A) edge node[left]{$I$} (B)
(C) edge node[right]{$O$} (B);
the horizontal 1-cell $\mathbb{G}(N)$ is given by:
(A) edge node[left]{$\tau_c L(I)$} (B)
(C) edge node[right]{$\tau_c L(O)$} (B);
and then the horizontal 1-cell $\mathbb{E} \mathbb{G}(N)$ is given by:
\node (D) at (1,-0.5) {$d \in F(R(d))$};
(A) edge node[left]{$R(\tau_c)I$} (B)
(C) edge node[right]{$R(\tau_c)O$} (B);
Then we can find a 2-isomorphism $\epsilon_N \colon \mathbb{E} \mathbb{G} (N) \xrightarrow{\sim} N$ in $\mathbb{F}\textnormal{Cospan}(\bold{C})$ given by:
\node (D) at (1,0.5) {$d \in F(R(d))$};
\node (D') at (1,-1.5) {$d \in F(c)$};
(A) edge node[above]{$R(\tau_c)I$} (B)
(C) edge node[above]{$R(\tau_c)O$} (B)
(A') edge node[above]{$I$} (B')
(C') edge node[above]{$O$} (B')
(B) edge node [left]{$e$} (B')
$$\iota \colon F(e)(d) \to d$$
\section{An example}
As an example, let $L \colon \bold{FinSet} \to \bold{Graph}$ be the functor which is left adjoint to the forgetful functor $R \colon \bold{Graph} \to \bold{FinSet}$; the functor $L$ maps a finite set $N$ to the discrete graph with $N$ as its set of vertices and no edges. Since $\bold{Graph}$ is a topos and thus has finite colimits, we can then obtain a symmetric monoidal double category $_L \mathbb{C}\textnormal{sp}(\bold{Graph})$ which has:
\item{finite sets as objects,}
\item{functions as vertical 1-morphisms,}
\item{cospans of graphs of the form
as horizontal 1-cells, where $L(N)$ and $L(N^\prime)$ are discrete graphs on the sets $N$ and $N^\prime$, respectively, $M$ is a graph and $i$ and $o$ are graph morphisms, and}
\item{maps of cospans of graphs of the form
as 2-morphisms, where $L(f)$ and $L(g)$ are maps of discrete graphs given by the underlying functions $f$ and $g$, respectively, and $h \colon M \to M^\prime$ is a graph morphism.
